\Huge \textcolor{titleTextColor}{ \textsf{ \fontsize{130}{100}\selectfont \textbf{GRASS}\,{\firalight GIS}: A General-purpose Geospatial Research Tool } }

### 2018-11-30 grassposter/2018_AGU_Geospatial_Research_Tool/poster.tex
poster: take home message, further shorten, swap boxes
git-svn-id: https://svn.osgeo.org/grass/grass-promo@73726 15284696-431f-4ddb-bdfa-cd5b030d7da7

@@

\node[above left,opacity=0.99,inner sep=0pt,outer sep=4cm] at (bottomleft -| topright)%
  {\includegraphics[width=0.2\paperwidth]{grass}};

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Overview and Functionality}}{

\LARGE

\begin{itemize}
% Basic Topics
 \item Community-driven project
 \item 35 years of continuous software development
 \item long-term releases, stable APIs, and emphasis on science
 \item single integrated environment for 2D and 3D raster analysis, image processing, vector data analysis, and spatio-temporal data processing
% GRASS GIS
% distribution strives to provide single integrated environment for 2D and 3D
% raster analysis, image processing, vector data analysis, and spatio-temporal
% data processing. It supports large raster files (billions of cells), vector
% topology, coupling with databases, and 64 bit memory.
%  \item To support the needs of scientists, the documentation includes not only links to the source code, its history, and
% its authors, but also links to research papers that describe the algorithms
% implemented in the modules.
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Code Life Cycle}}{

@@

\begin{itemize}
 \item New code based on recent research is typically contributed to GRASS GIS Addons repository.
 \item Mature, widely used code is then moved to the main code base to maximize integration and availability.
 \item Both main code base and Addons maintained by the community.
 \item Code preserved in long term even in cases when the original author no longer supports the code.
\end{itemize}

@@

\begin{itemize}
 \item The time dimension was introduced in version 7.0 \citep{Gebbert20141, gebbert2015grass}
 \item Time series accessed as space time datasets and as individual vectors or rasters.
 \item More than 50 modules available to manage, analyze, process, and visualize space time datasets.
 \item More than 100,000 map layers can be now handled efficiently in GRASS GIS.
 \item Used for analysis of the European Climate Assessment \& Dataset ECA\&D \citep{Haylock2008_climate_series}
       and temperate climate zone identification \citep{Gebbert20141}.
 \item New temporal modules (e.g. \gmodule{t.rast.aggregate}) work beside well established \gmodule{r.series} module
       and specialized modules such as \gamodule{r.hants} implemented according to \cite{roerink2000reconstructing} or \gamodule{r.seasons}.
 \item Raster and vector temporal algebra can be used for tasks
       such as computing hydrothermal coefficient for a time series of climate data using the actual mathematical formula
       \citep{leppelt2015grass}.
\end{itemize}

\begin{itemize}
 \item The \gmodule{r.sim.water} simulation model \citep{Mitas1998b}
for overland flow with spatially variable rainfall excess conditions was integrated into the Emergency
Routing Decision Planning system as a WPS \citep{raghavan2014deploying}.
% TODO: paralelized
\item A unique least cost path algorithm which doesn't need any depression filling
was implemented in \gmodule{r.watershed} module in 1989
and it was updated for massive data sets in 2011.
% TODO: refs
\item The \gmodule{r.sim.water} module was also utilized by \cite{Petrasova2014} and is now part of
\emph{Tangible Landscape}, a tangible GIS system, which also incorporated \gmodule{r.damflood},
a dam break inundation simulation by \cite{cannata2012two}.
\end{itemize}

\begin{minipage}{0.485\linewidth}
\centering
\includegraphics[width=0.7\textwidth]{rsimwater_architects}
\end{minipage}
~
\begin{minipage}{0.485\linewidth}
\includegraphics[width=\textwidth]{damflood_tangible}
\end{minipage}

\begin{minipage}{0.485\linewidth}
\centering
Overland flow simulated by \gmodule{r.sim.water} used for landscape
architecture design in Tangible Landscape environment
(Historical master plan for Lake Raleigh, NC, USA)
\end{minipage}
~
\begin{minipage}{0.49\linewidth}
Dam breach on Lake Raleigh (NC, USA) in Tangible Landscape environment simulated using \gamodule{r.damflood} module
\end{minipage}

@@

@@

\begin{itemize}
 \item \gamodule{r.smooth.seg} was created by Alfonso Vitti \citep{vitti2008free, vitti2012mumford} and implemented a piece-wise smooth approximation of the original image which can be used to reduce noise in the original image.
% according to \cite{mumford1989optimal} and \cite{march1997variational}
 \item \gmodule{r.clump} for grouping pixels with the same integer values available since 1980s.
       The latest version of \gmodule{r.clump} supports multiple image bands and clumping of floating point values.
 \item Eric Momsen implemented region-growing image segmentation in 2012.
       Markus Metz then extended and optimized the code resulting in the inclusion of the \gmodule{i.segment} module into version 7.0.
       This replaced a multi-resolution classification module of the same name from 1992 \citep{zhuang1992image}.
 \item \gamodule{i.segment.hierarchical} by Pietro Zambelli is based on \gmodule{i.segment} and performs parallelized hierarchical segmentation.
 \item Rashad Kanavath and Markus Metz implemented SLIC Superpixels segmentation \citep{achanta2010epfl, achanta2012slic} in 2016 as \gmodule{i.superpixels.slic}.
\end{itemize}

@@

\scriptsize

@@

\begin{itemize}
 \item Filtering of ground and non-ground points was included
early on in the lidar era in the \gmodule{v.lidar.edgedetection} group of modules.
% TODO: ref
% v.lidar.correction Corrects the v.lidar.growing output. It is the last of the three algorithms for LIDAR .
% v.lidar.edgedetection Detects the object's edges from a LIDAR data set.
% v.lidar.growing Building contour determination and Region Growing algorithm for determining the building inside
 \item The module \gmodule{v.surf.rst} for spatial interpolation was developed approximately 20 years
ago, but since then it has been improved several times \citep{tracvsurfrst}
including recent parallelization which will be included in GRASS GIS 7.4.
% TODO: ref for paralelized
 \item The module \gmodule{r.in.lidar} statistically analyzes massive point clouds.
% TODO: base_raster, ref
 \item The \gmodule{v.outlier} module serves as a base for a module \gamodule{v.lidar.mcc} implementing Multiscale Curvature Classification.
% TODO: ref
\end{itemize}

% v.delaunay v.voronoi New option to create Voronoi diagrams for areas.

\centering
\begin{minipage}{0.48\linewidth}
\centering
\includegraphics[width=0.7\textwidth]{elevation_lidar}
\end{minipage}
~
\begin{minipage}{0.48\linewidth}
\centering
\includegraphics[width=\textwidth]{lidar_profile}
\end{minipage}

\begin{minipage}{0.48\linewidth}
\centering
Digital elevation model interpolated from lidar data shows tillage in an field in Raleigh, NC, USA
\end{minipage}
~
\begin{minipage}{0.48\linewidth}
\centering
Vertical slice of a point cloud created with \gamodule{v.profile.points} shows tree structure in lidar data
\end{minipage}

>>>>

\usepackage{setspace}

@@

\node[above left,opacity=0.99,inner sep=0pt,outer sep=6cm] at (bottomleft -| topright)%
  {\includegraphics[width=0.2\paperwidth]{grass}};

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Why GRASS GIS as a Tool?}}{

Multiple researchers for over three decades
contributed code,
published associated papers,
implemented other's papers
and improved and built on each others work.

\includegraphics[width=\linewidth]{grass_team}

\begin{itemize}
% Basic Topics
 \item Community-driven project
 \item Long-term releases, stable APIs and emphasis on science
 \item Single integrated environment for 2D and 3D raster analysis, image processing, vector data analysis and spatio-temporal data processing
% GRASS GIS
% distribution strives to provide single integrated environment for 2D and 3D
% raster analysis, image processing, vector data analysis and spatio-temporal
% data processing. It supports large raster files (billions of cells), vector
% topology, coupling with databases and 64 bit memory.
%  \item To support the needs of scientists, the documentation includes not only links to the source code, its history and
% its authors, but also links to research papers that describe the algorithms
% implemented in the modules.
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Why GRASS GIS as a Platform?}}{

@@

Contributed code is maintained and extended by community
and prevails even in cases when the original author cannot support its users.

\begin{itemize}
 \item New code typically contributed to Addons repository.
 \item Mature code is moved to the main code base.
 \item Both main code base and Addons maintained by the community.
\end{itemize}

@@

@@

\begin{itemize}
 \item The time dimension was introduced in version 7.0 \citep{Gebbert20141, gebbert2015grass}
 \item Time series accessed as space time datasets and as individual vectors or rasters.
 \item More than 50 modules available to manage, analyze, process and visualize space time datasets.
 \item More than 100,000 map layers can be now handled efficiently in GRASS GIS.
 \item Used for analysis of the European Climate Assessment \& Dataset ECA\&D \citep{Haylock2008_climate_series}
       and temperate climate zone identification \citep{Gebbert20141}.
 \item New temporal modules (e.g. \gmodule{t.rast.aggregate}) work beside well established \gmodule{r.series} module
       and specialized modules such as \gamodule{r.hants} implemented according to \cite{roerink2000reconstructing} or \gamodule{r.seasons}.
 \item Raster and vector temporal algebra can be used for tasks
       such as computing hydrothermal coefficient for a time series of climate data using the actual mathematical formula
       \citep{leppelt2015grass}.
\end{itemize}

\scriptsize
\setstretch{0.5}

@@

\begin{itemize}
% according to \cite{mumford1989optimal} and \cite{march1997variational}
 \item \gmodule{r.clump} for grouping pixels with the same integer values available since '80s.
       Now \gmodule{r.clump} handles multiple image bands and floating point values.
 \item \gamodule{r.smooth.seg} for noise reduction \citep{vitti2008free, vitti2012mumford}
 \item Region-growing image segmentation originally from Eric Momsen (2012)
       was improved by Markus Metz and included as \gmodule{i.segment} into version 7.0.
%        This replaced a multi-resolution classification module of the same name from 1992 \citep{zhuang1992image}.
 \item \gamodule{i.segment.hierarchical} by Pietro Zambelli based on \gmodule{i.segment} performs parallelized hierarchical segmentation.
 \item Rashad Kanavath and Markus Metz implemented SLIC Superpixels segmentation \citep{achanta2010epfl, achanta2012slic} in 2016 as \gmodule{i.superpixels.slic}.
\end{itemize}

@@

\begin{itemize}
 \item \gmodule{r.sim.water} module \citep{Mitas1998b}
       for simulating overland flow integrated into the Emergency Routing Decision Planning \citep{raghavan2014deploying}.
% TODO: paralelized
 \item \gmodule{r.watershed} for least cost path water accumulation from 1989
       and updated for massive data sets in 2011.
% TODO: refs
 \item \cite{Petrasova2014} utilized in \emph{Tangible Landscape}, a tangible GIS system,
       \gmodule{r.damflood}, a dam break inundation simulation by \cite{cannata2012two}.
\end{itemize}

% \bigskip

% \vspace*{0.5cm}

\begin{minipage}{0.485\linewidth}
\centering
\includegraphics[width=0.7\textwidth]{rsimwater_architects}
\end{minipage}
~
\begin{minipage}{0.485\linewidth}
\includegraphics[width=\textwidth]{damflood_tangible}
\end{minipage}
\vspace{2mm}
\begin{center}
Overland flow simulated used for landscape
architecture design in Tangible Landscape environment (left)
and a dam breach on Lake Raleigh, NC, USA (right)
\end{center}

@@

\begin{itemize}
 \item Filtering of ground points was included
       in the \gmodule{v.lidar.edgedetection} group of modules.
% TODO: ref
% TODO: year
% v.lidar.correction Corrects the v.lidar.growing output. It is the last of the three algorithms for LIDAR .
% v.lidar.edgedetection Detects the object's edges from a LIDAR data set.
% v.lidar.growing Building contour determination and Region Growing algorithm for determining the building inside
 \item \gmodule{v.outlier} module serves as a base for a module \gamodule{v.lidar.mcc} implementing Multiscale Curvature Classification.
% TODO: ref
 \item \gmodule{v.surf.rst} (spatial interpolation) for developed in '90s;
       improved several times and parallelized for version 7.4.
% \citep{tracvsurfrst}
% TODO: different ref
% TODO: ref for paralelized
 \item Improved \gmodule{r.in.lidar} statistically analyzes large point clouds.
% TODO: base_raster, ref

\end{itemize}

\centering
\begin{minipage}{0.4\linewidth}
\centering
\includegraphics[width=0.7\textwidth]{elevation_lidar}
\end{minipage}
~
\begin{minipage}{0.55\linewidth}
\centering
\includegraphics[width=\textwidth]{lidar_profile}
\end{minipage}
\vspace{2mm}
\begin{center}
Digital elevation model interpolated from lidar data shows tillage in an field in Raleigh, NC, USA
and a point cloud transect created with \gamodule{v.profile.points} shows tree structure
\end{center}
